Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-01 draft/paper1_jenny.tex
Edit summary 1

    In this work, we study how environment (halo mass) affects the stellar mass density 
    profiles of massive central galaxies using deep images from the Subaru HSC 
    survey. 
    With the help of this high-quality and wide area data set, we directly map the 
    stellar mass distributions of ${\sim}7000$ massive central galaxies at 
    $0.3 < z < 0.5$ out to $>100$ kpc without resorting to stacking techniques. 
    We group massive central galaxies into two categories based on their host halo 
    mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and \mhalo{}$\simlt 10^{14} M_{\odot}$). 
    Our main results are:

    \begin{enumerate}
        \item We find that the ``total'' \mstar{} of these massive galaxies can be 
            significantly underestimated with shallow imaging data such as SDSS and/or 
            imperfect model assumption (e.g. the \texttt{cModel} or single-\ser{}) 
            are used. 
            In contrast to previous work, our results do not depend on stacking or any 
            parametric models. 
            Moreover, the level of such underestimation could also depend on the 
            stellar mass and on halo mass. 
            This should be carefully taken into account when discussing topics such 
            as the evolution of the galaxy SMF.

>>>>

    In this work, we study how the stellar mass density profiles and other structural
    properties of massive central galaxies depend on their total stellar mass using 
    deep images from the Subaru HSC survey. 
    With the help of this high-quality and wide area data set, we directly map the 
    stellar mass distributions of ${\sim}7000$ massive central galaxies at 
    $0.3 < z < 0.5$ out to $>100$ kpc without resorting to stacking techniques. 
    We group massive central galaxies into two categories based on their host halo 
    mass (\mhalo{}$\simgt 10^{14.0} M_{\odot}$ and \mhalo{}$\simlt 10^{14} M_{\odot}$)
    and three bins of \mtot{}.  
    Our main results are:

    \begin{enumerate}
        \item We find that the ``total'' \mstar{} of these massive galaxies can be 
            significantly underestimated with shallow imaging data such as SDSS and/or 
            oversimplified model assumption (e.g. the \texttt{cModel} or single-\ser{}). 
            In contrast to previous work, our results do not depend on stacking or any 
            parametric models. 
            Moreover, the level of such underestimation also depends on their \mtot{}.
            More massive galaxies tend to have larger amount of light missing in the 
            outskirt.  
            The level of underestimation also shows evidence of \mhalo{}-dependence. 
            The central galaxies of \mhalo{}$\simgt 10^{14.0} M_{\odot}$ halos suffer
            more from this issue. 
            This should be carefully taken into account when discussing topics such 
            as the evolution of the galaxy SMF.
